---
title: "Outlines objectives and results"
author: "K. Kraskura"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<br/>

#### OBJECTIVES: compare two bioaccumulation food web models. 

1. [Liang et al 2022](http://dx.doi.org/10.1016/j.scitotenv.2022.156397)
2. [Sun et al 2022](https://pubs.rsc.org/en/content/articlelanding/2022/em/d2em00047d)

##### Some model equations, and changes:

1. k_1 calculated the same: 
  + Liang et al: 0.0021
2. k_G = *GRF* * W_B^(-0.2); the same in both models, but the coefficients are different
  + Liang et al has two based on the temperature 0.00251 at ~ 25 ºC, and 0.0005 for ~ 10 ºC. 
  + JBA summer: 0.0014 
  + GRF (growth rate factor) is different 
  + Sun et al: 0.0014
3. E_D = 1/ (5.1 * 10^(-8) K_ow+2)) *updated*
4. k_D = (F_D * E_D) / W  *same* (F_D = G_D; feeding rate)
5. k_2 = k_1 / (P_B * K_ow) *new in Liang et al* 
6. k_M = k_BT - k_BTR # new *new - not incorporated*
  + k_M = 0 # no other way to guess for us?    
  + k_BTR = k_2 + k_E + k_G # reference non biotranformed chemical 
  + k_BT = k_2 + k_E + k_G + k_M # biotransformed chemical 
  + k_M = k_BT - k_BTR # new 
7. k_E = 0.25 * k_D
8. E_W = 1 / (1.85 + (155 / K_ow)) *updated*
  + E_W = Fish gill uptake efficiency (%) 
  + *this is very different between models* (plotted below)
9. All fish were assumed to have 15% protein when applying Liang et al 2022 model. 
  
  
  
  
<br>

#### Key differences between the models






1. Liang et al 2022 model does not account for sediment uptake (part of diet) in fish. We don't have invertebrates in the food web, and so the link between sediment and fish is lost using this modeling approach. 
2. Sun et al 2022 includes renal elimination, but dont have metabolic biotransformation (set to 0). The Liang et al 2022 model does not have renal elimination, but has metbolic transformation for some of PFAS. To me it was not obvious how they calculated it, I set metabolic transformation to 0 for Liang et al 2022 too. 
3. The water uptake rate is directly dependent on fish gill uptake efficiency (%) (E_W), which is is substentially different between models. The potential cause of discrepancies/ place for improvement. 
4. In Liang et al 2022, the egestion as an elimination pathway is constant across all PFAS, 25% of the upatke via the diet. This should vary between PFAS?
5. Elimination rate through the gills, has differnet modeled mechanisms. Sun et al uses k_2 = k_1 / D_BW, where D_BW describes the total uptake of PFAS through the gut. Liang et al 2022 uses k_2 = k_1/ (P_B * K_ow), which directly depends on the protein content of the fish, and K[OW].

*! Modeled are JBA summer only*

```{r source, warning=FALSE, message=FALSE, echo=TRUE}

library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)
library(tibble) # needed to get named list of dataframes (in data_tables.R)
library(readxl)
library(ggformat2)

# functions to run food web model
source("../Code/PFAS_bioaccum_v2.R") 
source("../Code/PFAS_classes_v2.R")
source("../Code/PFAS_steadyState_v2.R")
source("../Code/runEcosystemModels.R") # custom written
source("../Code/runErrorEstimates.R")
source("../Code/data_tables.R")
source("../Code/PFAS_tissuePart_v2.R")

# source data tables for each objective
kRTable = read.csv('../Data/export_krTable.csv', row.names = "X", header = T)
colnames(kRTable)<-c("kr/kb", "PFAA", "chemID")

PFAS_List <- c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA')
PFAS_labels <- c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA','C11 PFCA')
PFAA_cols <- c('PFHxS' = '#332288', # 
             'PFOS' = '#882255', # 
             'PFOA' = '#117733',
             'PFNA' = '#88CCEE',
             'PFDA' = 'orange',
             'PFUA' = '#AA4499')

p_lines <- data.frame('x' = c(0, 7),
                      'y' = c(0, 7))
p_lines$y1 <- p_lines$x-1
p_lines$y2 <- p_lines$x+1
p_lines$y3 <- p_lines$x-log10(2)
p_lines$y4 <- p_lines$x+log10(2)

```

<br/>

```{r jba sum1 Liang et al, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, fig.align= 'center'}
source("../Code/data tables/JBA_data_sum_Liang.R")

settings_obsDiet = new_Settings(
  chooseStudyType = 'default',
  chooseDiet = 'forced',
  chooseKoc = 'Koc',
  chooseRenal ='off',
  chooseEw = 'beta0', # this is new for Liang et al
  chooseModel = 'Liang_etal_2022'
)


AllDataJBAsum<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s','k1','k2','ke','kg','kd',
                                    'Total Elimination', 'RMR', "Gill_uptake", 
                                    "Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", "Sed_up%",
                                    "Total Elimination", "G_V", "G_D",
                                     'k1' , 'k2', 'kd' , 'ke' , 'kg', 'kr_est', "Ew"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  run_w_RenalElim = TRUE,
                  food_web_calc = TRUE,
                  min_diet_WTO_C_s = FALSE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = FALSE, 
                  max_dietData = inputFiles_list$max_dietData)


settings_modelDiet = new_Settings(
  chooseStudyType = 'default',
  chooseDiet = 'default',
  chooseKoc = 'Koc',
  chooseRenal ='off',
  chooseModel = "Liang_etal_2022",
  chooseEw = "beta0"
)

AllDataJBAsum_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s','k1','k2','ke','kg','kd',
                                    'Total Elimination', 'RMR', "Gill_uptake",
                                    "Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", "Sed_up%",
                                    "Total Elimination", "G_V", "G_D",
                                     'k1' , 'k2', 'kd' , 'ke' , 'kg', 'kr_est', "Ew"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  run_w_RenalElim = TRUE,
                  food_web_calc = TRUE,
                  min_diet_WTO_C_s = FALSE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = FALSE, 
                  max_dietData = inputFiles_list$max_dietData)

AllDataJBAsum <- AllDataJBAsum[!c(AllDataJBAsum$PFAA == "PFUA" ),]
AllDataJBAsum_fw <- AllDataJBAsum_fw[!c(AllDataJBAsum_fw$PFAA == "PFUA" ),]

AllData_Liang <- AllDataJBAsum
AllData_fw_Liang <- AllDataJBAsum_fw



```

```{r jba sum Sun et al , echo = FALSE, message=FALSE, warning=FALSE}
source("../Code/data tables/JBA_data_sum_Liang.R")

settings_obsDiet = new_Settings(
  chooseStudyType = 'default',
  chooseDiet = 'forced',
  chooseKoc = 'Koc',
  chooseRenal ='off',
  chooseModel = 'Sun_etal_2022'
  # ew is empirically tested
)


AllDataJBAsum<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s','k1','k2','ke','kg','kd',
                                    'Total Elimination', 'RMR', "Gill_uptake", 
                                    "Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", "Sed_up%",
                                    "Total Elimination", "G_V", "G_D",
                                     'k1' , 'k2', 'kd' , 'ke' , 'kg', 'kr_est', "Ew"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  run_w_RenalElim = TRUE,
                  food_web_calc = TRUE,
                  min_diet_WTO_C_s = FALSE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = FALSE, 
                  max_dietData = inputFiles_list$max_dietData)


settings_modelDiet = new_Settings(
  chooseStudyType = 'default',
  chooseDiet = 'default',
  chooseKoc = 'Koc',
  chooseRenal ='off',
  chooseModel = "Sun_etal_2022"
)

AllDataJBAsum_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s','k1','k2','ke','kg','kd',
                                    'Total Elimination', 'RMR', "Gill_uptake",
                                    "Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", "Sed_up%",
                                    "Total Elimination", "G_V", "G_D",
                                     'k1' , 'k2', 'kd' , 'ke' , 'kg', 'kr_est', "Ew"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  run_w_RenalElim = TRUE,
                  food_web_calc = TRUE,
                  min_diet_WTO_C_s = FALSE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = FALSE, 
                  max_dietData = inputFiles_list$max_dietData)

AllDataJBAsum <- AllDataJBAsum[!c(AllDataJBAsum$PFAA == "PFUA" ),]
AllDataJBAsum_fw <- AllDataJBAsum_fw[!c(AllDataJBAsum_fw$PFAA == "PFUA" ),]

AllData_Sun <- AllDataJBAsum
AllData_fw_Sun <- AllDataJBAsum_fw



# legend<-cowplot::get_legend(legend_plot)
# fig1<-cowplot::plot_grid(p1, p2, legend,
#                    ncol = 3,
#                    nrow = 1,
#                    rel_widths = c(1,1, 0.3),
#         labels = c("Empirical PFAS in diet", "Modeled PFAS in diet", ""))


```


##### Model predictions  

```{r setup2, echo = FALSE}
AllData_Sun$model<-"Sun et al 2022"
AllData_fw_Sun$model<-"Sun et al 2022"

AllData_Liang$model<-"Liang et al 2022"
AllData_fw_Liang$model<-"Liang et al 2022"

d<-rbind(AllData_Sun, AllData_Liang)
d_fw<-rbind(AllData_fw_Sun, AllData_fw_Liang)

```

```{r plot diet plot1, fig.width=5, fig.height=5}
p1<-ggplot(data = d, aes(x = log_ngkg_re, y = Obs_logngkg,
                         color = PFAA,
                         shape = model))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y, shape = NULL),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    # geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo,
    #                   ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    # geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo,
    #                    xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(size = 3)+
    scale_shape_manual(values = c(19, 17))+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'Given PFAA diet values')+
    coord_cartesian(ylim = c(1,7), xlim = c(1,7))

ggformat(p1, y_title = ('Measured log PFAS (ng/kg)'), x_title = 'Modeled log PFAS (ng/kg)', size_text = 12, print = F)
p1<-p1+theme(legend.position = "none")

# p1_fish
```

```{r plot diet plot2, fig.width=5, fig.height=5}
p2<-ggplot(data = d_fw, aes(x = log_ngkg_re, y = Obs_logngkg,
                            color = PFAA,
                            shape = model))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y, shape = NULL),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    # geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo,
    #                   ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    # geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo,
    #                    xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(size = 3)+
    scale_shape_manual(values = c(19, 17))+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = '')+
    coord_cartesian(ylim = c(1,7), xlim = c(1,7))

ggformat(p2, y_title = ('Measured log PFAS (ng/kg)'), x_title = 'Modeled log PFAS (ng/kg)', size_text = 12, print = F)
p2<-p2+theme(legend.position = "right")

legend<-cowplot::get_legend(p2)
p2<-p2+theme(legend.position = "none")
```



```{r legend and saving, fig.width=10, fig.height=4.5}
fig1<-cowplot::plot_grid(p1, p2, legend,
                   ncol = 3,
                   nrow = 1,
                   rel_widths = c(0.9,0.9, 0.3),
                   label_x = c(0, 0, 0),
                   label_y = c(0.9, 0.9, 0.9),
                   label_size = 12,
        labels = c("known PFAS in diet", "modeled PFAS in diet", ""))
fig1

ggsave(filename = "../Figures/fig1_model_comparison_nov22.png", plot = fig1, height = 4, width = 9)

```


```{r ew gill uptake efficiency }

ggplot(d, aes(x = PFAA , y = Ew, group = model, shape=model))+
  geom_point(size=3)+
  scale_shape_manual(values = c(19, 17))+
  ylab("fish gill uptake efficiency (%)")

```

##### Proportions of diet uptake. 

```{r water vs gill, echo = FALSE, message = FALSE, warning  = FALSE, fig.height = 15, fig.width = 10, fig.align = "center", eval = TRUE}
# stackbar dataset
AllData_m<-melt(d[, c("SppAlias", "PFAA", "Gill_up%", "Diet_up%", "Sed_up%", "WB", "C_WTO", "C_s", "model")], id.vars=c("SppAlias", "PFAA", "WB", "C_WTO", "C_s", "model"))

# summarize means for % uptake for each run
mean_d_pct<-AllData_m %>%
dplyr::group_by(PFAA, SppAlias, variable, C_WTO, C_s, WB, model) %>%
summarize(mean_pct = mean(value),
          sd_pct = sd(value)) 

mean_d_pct_m<-mean_d_pct %>% 
  dplyr::group_by(PFAA, variable, C_WTO, C_s, model) %>%
  summarize(mean_pct = mean(mean_pct),
          sd_pct = sd(mean_pct)) 
  
# summarize actual values 
mean_d<-d %>%
dplyr::group_by(PFAA, SppAlias, model) %>%
summarize(Gill = mean(`Gill_uptake`),
          Diet = mean(`Dietary_uptake`),
          Sediment = mean(`Sediment_uptake`),
          Elimination = mean(`Total Elimination`), 
          WB = mean(WB)) %>%
pivot_longer(cols = c(Gill, Diet, Sediment, Elimination), names_to = "Path", values_to = "Uptake_g.kg.day")

mean_sd<-d %>%
dplyr::group_by(PFAA, SppAlias, model) %>%
summarize(Gill = sd(`Gill_uptake`),
          Diet = sd(`Dietary_uptake`),
          Sediment = sd(`Sediment_uptake`),
          Elimination = sd(`Total Elimination`),
          WB = mean(WB)) %>%
pivot_longer(cols = c(Gill, Diet, Sediment, Elimination), names_to = "Path", values_to = "Uptake_SD_g.kg.day")

AllData_m2 <- merge(mean_d, mean_sd, all.x = TRUE, by = c("PFAA", "SppAlias", "Path", "WB", "model"))


ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy", ], aes( x=mean_pct*100, y=SppAlias,
                                                         color = variable,
                                                         fill = variable)) + 
    geom_bar(stat="identity", position = "stack", color = "black", stroke = 0.1) +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_wrap(PFAA~model, scales = "free", nrow=5)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#44C08A", "#00C2FF", "brown"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
  ylab("Species")+
  xlab("% Uptake")+
  theme_bw()+
  theme(legend.position = "top")
```

```{r diet to water uptake, fig.height = 10, fig.width = 6, fig.align = "center", eval = FALSE}

p_diet_water<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy", ],
       aes( x=mean_pct*100, y=SppAlias,
            color = variable,
            fill = variable)) + 
    geom_bar(stat="identity", position = "stack",
             color = "black",
             stroke = 0.3)+
    facet_wrap(.~PFAA, scales = "free", nrow =5)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#44C08A", "#00C2FF", "brown"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
  scale_y_discrete(breaks = c("Swa",
                              "Pum",
                              "Min",
                              "Mad",
                              "Fal",
                              "Dar",
                              "Dac",
                              "Bas"), 
                   labels = c("Swallowtail Shiner",
                              "Pumkinseed",
                              "Mudminnow",
                              "Margined Madtom",
                              "Fallfish",
                              "Darter sp.",
                              "Dace sp.",
                              "Largemouth Bass"))+
  ylab("Species")+
  xlab("% Uptake")+
  theme_bw()+
  theme(legend.position = "right")

ggformat(p_diet_water, y_title = 'Species', x_title = "% Uptake", title = "JBA summer", size_text = 12)
p_diet_water<-p_diet_water+ theme(legend.position = "right")
ggsave(filename = "../Figures/fig8_deit_water_now1.png", plot = p_diet_water, height = 10, width = 5)



```

<br>

##### Different elimination pathways 

```{r elim rates, echo = FALSE, message = FALSE, warning  = FALSE, fig.height = 15, fig.width = 10, fig.align = "center", eval = TRUE}
# stackbar dataset
AllData_k<-melt(d[, c("SppAlias", "PFAA", "k2", "ke", "kg", "WB", "C_WTO", "C_s", "model")], id.vars=c("SppAlias", "PFAA", "WB", "C_WTO", "C_s", "model"))

# summarize means for % uptake for each run
mean_d_k<-AllData_k %>%
dplyr::group_by(PFAA, SppAlias, variable, C_WTO, C_s, WB, model) %>%
summarize(mean_k = mean(value),
          sd_k = sd(value)) 
  

AllData_m2 <- merge(mean_d, mean_sd, all.x = TRUE, by = c("PFAA", "SppAlias", "Path", "WB", "model"))


ggplot(mean_d_k[!mean_d_k$SppAlias == "Phy", ], aes( x=(mean_k), y=SppAlias,
                                                         color = variable,
                                                         fill = variable)) + 
    geom_bar(stat="identity", position = "stack", color = "black", stroke = 0.1) +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_wrap(PFAA~model, scales = "free", nrow=5)+
    # scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#44C08A", "#00C2FF", "brown"),
    #                   labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
  ylab("Species")+
  xlab("% Uptake")+
  theme_bw()+
  theme(legend.position = "top")
```

```{r fig chain length diet, fig.height = 10, fig.width = 6, fig.align = "center", eval = FALSE}


```


##### Dietary uptake and chain length 

```{r chain length and accumulation, fig.height = 4.5, fig.width = 10, fig.align = "center", eval = TRUE}
PFAA_List <- data.frame(PFAA = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'), PFAA_labels = c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA','C11 PFCA'), PFAA_n = c(6,8,8,9,10,11))

d<-merge(d, PFAA_List, by = "PFAA")
d$PFAA_labels<-factor(d$PFAA_labels)
d$PFAA_labels<-factor(d$PFAA_labels, levels = c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA'))

d_chainleng<-ggplot(d, aes(y=`Diet_up%`, x = PFAA_n,
              color = PFAA,
              shape = model,
              group = model))+
  geom_point(size = 2)+
  # geom_point( mapping = aes(y = Obs_logngkg, x = PFAA_labels,
  #               color = PFAA,
  #               shape = model),
  #            position = position_dodge(width = 0.3, preserve = "single"),
  #            size = 2, alpha = 0.4)+
  facet_grid(.~model)+
  geom_smooth(method = "lm", fill = "grey90", color = "black")+
  scale_color_manual(values = PFAA_cols)+
  scale_shape_manual(values = c(19, 17))+
  theme_bw()+
  xlab("PFAA chain length")+
  theme(axis.text.x = element_text(angle = 0))

ggformat(d_chainleng, x_title = "PFAA chain length", y_title = 'Dietary uptake %',
         size_text = 12, print = T)

# ggsave(filename = "../Figures/fig2_chainLen_oct31.png", plot = d_chainleng, height = 3.5, width = 5.5)


```

