---
title: "Data Tables"
subtitle: "Willow Grove, Joint Base Andrew's (JBA) (spring and summer)"
author: "Krista Kraskura"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false
      smooth_scroll: false
---
```{css echo = FALSE, include = FALSE}
li {
  line-height: 1;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r source files, echo = FALSE, message=FALSE}

library(gridExtra)
library(kableExtra)
library(here)
# here::set_here(path = "../../")

source(here("Code/R model/data_tables.R"))

source(here("Code/R data tables/WG.R"))
data.wg<-inputFiles_list
source(here("Code/R data tables/JBA_spring.R"))
data.jba.sp<-inputFiles_list
source(here("Code/R data tables/JBA_summer.R"))
data.jba.sum<-inputFiles_list

```


Source code to construct data tables: `"./data_tables.R"`.
(Use:`rmarkdown::render("./data_tables.R")` to see it as rendered html)

## Tables and variable definitions

**1. Organism Data**

*Description*:

*Definitions*:

-   WB = body weight
-   m_O = Fraction of respiration from overlying water
-   nu_NB = Neutral lipid fraction in the gut
-   nu_LB = Phospholipid fraction in the gut
-   nu_PB = Binding protein fraction in the gut
-   nu_OB = NLOM fraction in the gut
-   nu_WB = Water fraction in the gut
-   epsilon_N = Neutral lipid absorption efficiency
-   epsilon_L = Phospholipid absorption efficiency
-   epsilon_P = Protein absorption efficiency
-   epsilon_O = NLOM (Non Lipid Organic Matter) absorption efficiency
-   epsilon_W = Water absorption efficiency
-   A = Resistance to chemical uptake through the aqueous phase of phytoplankton
-   B = Resistance to chemical uptake through the organic phase of phytoplankton
-   GRF = Growth rate factor
-   switches = variable to choose appropriate k_1, G_D, and k_r calculations for different taxa
-   MMR = maximum metabolic rate; mg O2 / day; if NA MMR is estimated 
-   RMR = resting metabolic rate; mg O2 / day; if NA RMR is estimated 
-   pct_FeedRate = percent feeding rate


<br>

**2. Chemical (ecosystem) data**

*Description*:

*Definitions*:

-   C_WTO = Chemical concentration in overlying water
-   C_s = Contaminant concentration in sediment
-   Phi_exp = Chemical fraction in the dissolved phase

<br>

**3. Ecosystem data**

*Description*:

*Definitions*:

-   C_OX = Dissolved oxygen concentration
-   T = Temperature
-   OCS Organic carbon content of the sediment
-   C_SS = Concentration of suspended solids

<br>

**4. Chemical (PFAA) parameters**

*Description*:

*Definitions*:

-   Log_Kow = octanol-water partition coefficient; COSMOtherm 2011; Armitage et al 2013, Environ. Toxicol. Chem. 2013, 32 (1), 115--128. <https://doi.org/10.1002/etc.2020>.
-   pKa = acid strength; Calculated using Kow and Armitage et al 2013, Environ. Toxicol. Chem. 2013, 32 (1), 115--128. <https://doi.org/10.1002/etc.2020>.
-   log_Kpw = protein-water partition coefficient
-   log_Dmw = membrane-water partition coefficient (see Sun et al 2022 Table S3a)
-   E_D = Chemical absorption efficiency across the gill membrane (aqueous chemical absorption efficiency)
-   E_W = Fish gill uptake efficiency (%) calculated at Cox = 10 mg/L and T=12 (DO sat approximately 92%)
-   log_Koc = Organic carbon partitioning coefficient; Koc = Kd / OCS
-   chemID = chemical chain length

**5. Food Web**

-   Species consuming = rows
-   Species consumed = columns

**6. PFAA levels in each food item**

*Description*:
This table contains known (measured) PFAA concentration in each organism. 

<br>

## Data Tables
### 1. Organism data
#### 1.1. Willow Grove
```{r echo = FALSE, warning=FALSE}
data.wg[[2]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")
```
#### 1.2. JBA spring
```{r echo = FALSE, warning=FALSE}
data.jba.sp[[2]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")
```
#### 1.3. JBA summer
```{r echo = FALSE, warning=FALSE}
data.jba.sum[[2]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```


### 2. Chemical data
#### 2.1. Willow Grove
```{r echo = FALSE, warning=FALSE}

data.wg[[3]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 2.2. JBA spring
```{r echo = FALSE, warning=FALSE}

data.jba.sp[[3]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 2.3. JBA summer
```{r echo = FALSE, warning=FALSE}

data.jba.sum[[3]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```


### 3. Ecosystem data
#### 3.1. Willow Grove
```{r echo = FALSE, warning=FALSE}
data.wg[[4]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 3.2. JBA spring
```{r echo = FALSE, warning=FALSE}
data.jba.sp[[4]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 3.3. JBA summer
```{r echo = FALSE, warning=FALSE}
data.jba.sum[[4]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```



### 4. Chemical Paramaters
#### 4.1. Willow Grove
```{r echo = FALSE, warning=FALSE}
data.wg[[5]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 4.2. JBA spring
```{r echo = FALSE, warning=FALSE}
data.jba.sp[[5]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 4.3. JBA summer
```{r echo = FALSE, warning=FALSE}
data.jba.sum[[5]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```


### 5. Food Web
#### 5.1. Willow Grove
```{r echo = FALSE, warning=FALSE}
data.wg[[6]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 5.2. JBA spring
```{r echo = FALSE, warning=FALSE}
data.jba.sp[[6]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```
#### 5.3. JBA summer
```{r echo = FALSE, warning=FALSE}
data.jba.sum[[6]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```


### 6. PFAA levels in each food item
#### 6.1. Willow Grove
```{r echo = FALSE, warning=FALSE}
data.wg[[7]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")
```
#### 6.2. JBA spring
```{r echo = FALSE, warning=FALSE}
data.jba.sp[[7]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")
```
#### 6.3. JBA summer
```{r echo = FALSE, warning=FALSE}
data.jba.sum[[7]] %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Verdana")

```

