---
title: "Outlines objectives and results"
author: "K. Kraskura"
date: "`r Sys.Date()`"
output: 
  # pdf_document:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    toc_depth: 4
    theme: journal
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.align = "center")
```

<br/>


#### Fish food web bioaccumualtion model:

***Goal***:

To evaluate the model performance characterizing and predicting values in three samples systems (Joint Base Andrews, JBA, in spring and summer, and Willow Grove). In a given system, each species is described by the mean body size of all collected fish, and the system is described by the mean measured temperature, dissolved oxygen levels, organic carbon when available. No invertebrates were found or sampled in these systems.

***The model:***

The food web model is adapted from [Sun et al 2020](https://doi.org/10.1039/D2EM00047D).


***Metrics of model performance***:

1.  $R^2$ (full model, by PFAA, by Species)
  
$R^2 = 1-RSS / TSS$ 
  
$RSS = \sum (modeled_{val} - observed_{val}) $

$TSS = \sum (modeled_{val} - mean(observed_{val})) $

- RSS = residual sum squared
- TSS = total sum squared
  
2.  Model bias (MB) 

<!-- 2.1 Arnot and Gobas 2004.  -->

<!-- $MB_i = 10^{\frac{\sum_{i=1}^{n} log (C_{model, i} / C_{obs, i})}{n}}$ -->

<!-- $MB_j= 10^{\frac{\sum_{j=1}^{m} log (C_{model, j} / C_{obs, j})}{m}}$ -->

<!-- - n = number of chemicals in a given species -->
<!-- - m = number of species for a given chemical -->
<!-- - C[model] = predicted PFAA concentration -->
<!-- - C[obs] = observed PFAA concentration -->
<!-- - i = number of species -->
<!-- - j = number of chemicals -->

The method from: McLeod et al 2016. 

$MB_{avg} = (log(C_{avg-pred})/log(C_{avg-model}))$

$MB_{CV} = (log(C_{CV-pred})/log(C_{CV-model}))$

- C[avg-model] = average of predicted PFAA concentration for all organisms and all PFAS
- C[avg-obs] = average of observed PFAA concentration for all organisms and all PFAS
- CV = coefficients of variation (CV) 

```{r source, warning=FALSE, message=FALSE, echo=FALSE}

library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape)
library(tibble) # needed to get named list of dataframes (in data_tables.R)
library(readxl)
library(ggformat2)
library(here)
here::i_am(path = "./Code/R results/main_results_medianVals.Rmd")
# here()

# functions to run food web model
source(here("Code", "R model", "PFAS_bioaccum_v2.R"))
source(here("Code", "R model", "PFAS_classes_v2.R"))
source(here("Code", "R model", "PFAS_steadyState_v2.R"))
source(here("Code", "R model", "runEcosystemModels.R")) # custom written
source(here("Code", "R model", "runErrorEstimates.R")) # custom written 
source(here("Code", "R model", "data_tables.R"))
source(here("Code", "R model", "data_MonteCarlo.R")) # for sample size  
# source(here("Code", "R results", "fishbase_species_info.R")) # for sample size, source of fish_table

# source("../Code/PFAS_tissuePart_v2.R")

# source data tables for each objective
kRTable = read.csv(here("Data", 'export_krTable.csv'), row.names = "X", header = T)
colnames(kRTable)<-c("kr/kb", "PFAA", "chemID")

PFAS_List <- c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA')
PFAS_labels <- c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA','C11 PFCA')
PFAA_cols <- c('PFHxS' = '#332288', # 
             'PFOS' = "#C4A2D5", # 
             'PFOA' = '#117733',
             'PFNA' = '#88CCEE',
             'PFDA' = 'orange',
             'PFUA' = '#AA4499')

p_lines <- data.frame('x' = c(0, 7),
                      'y' = c(0, 7))
p_lines$y1 <- p_lines$x-1
p_lines$y2 <- p_lines$x+1
p_lines$y3 <- p_lines$x-log10(2)
p_lines$y4 <- p_lines$x+log10(2)

```

<br/>

#### 1. Willow Grove (fall/winter)

The model predictions for Willow Grove in fall winter seasons.

```{r willow grove fall}
source(here("Code", "R data tables", "WG_fallWinter.R")) # medians not same day

# PFAS are known in each diet item
settings_obsDiet = new_Settings(
  chooseDiet = 'forced', # known PFAA in diet
  chooseKoc = 'Koc',
  chooseDmw = "Droge",
  chooseEw = "empirical"
)

# # used below in sed:water est part 
# WG_inputFiles_list<-inputFiles_list
# water_WG<-d.water %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# water_WG<-water_WG/1000
# colnames(water_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# sed_WG<-d.sed %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# colnames(sed_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# obs_ratio_WG<-sed_WG/water_WG


# run the bioaccumulation model: 
AllDataWGfall<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet item are calculated from trophic transfer
settings_modelDiet = new_Settings(
  chooseDiet = 'default',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGfall_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet is set to zero
settings_modelDiet = new_Settings(
  chooseDiet = 'zero',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGfall_zero<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

```

```{r wg fall model bias tables, echo = FALSE, message=FALSE, warning=FALSE}

wg_fall1_error <- estimate_error(MetricData = AllDataWGfall, DataID = "wg_fall_forced", verbose = FALSE)
wg_fall1_error_fw <- estimate_error(MetricData = AllDataWGfall_fw, DataID = "wg_fall_fw", verbose = FALSE)
wg_fall1_error_zero <- estimate_error(MetricData = AllDataWGfall_zero, DataID = "wg_fall_zero", verbose = FALSE)

```

```{r willow fall grove data output and plots, fig.cap= "Figure. 1"}
# median value data
AllDataWGfall <- AllDataWGfall[!c(AllDataWGfall$PFAA == "PFUA" | AllDataWGfall$PFAA == "PFDA"),]
AllDataWGfall_fw <- AllDataWGfall_fw[!c(AllDataWGfall_fw$PFAA == "PFUA" | AllDataWGfall_fw$PFAA == "PFDA"),]
AllDataWGfall_zero <- AllDataWGfall_zero[!c(AllDataWGfall_zero$PFAA == "PFUA" | AllDataWGfall_zero$PFAA == "PFDA"),]

p1<-ggplot(data = AllDataWGfall, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 19, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'fall -forced diet')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_fall1_error[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_fall1_error[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")
p1

p2<-ggplot(data = AllDataWGfall_fw, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 19, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_fall1_error_fw[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MG[avg] == .(round(wg_fall1_error_fw[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    ggtitle(label = 'trophic diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")


p0<-ggplot(data = AllDataWGfall_zero, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 19, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'zero diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_fall1_error_zero[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_fall1_error_zero[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")


legend_plot <- ggplot(data = AllDataWGfall_fw,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)
fig1<-cowplot::plot_grid(p1, p2, p0, legend,
                   ncol = 2,
                   nrow = 2,
                   rel_widths = c(1,1),
        labels = c("A", "B", "C", ""))
fig1

ggsave(filename = here("./Figures/WG_fall_fig1.png"), width = 7, height = 7)

```

PFAS predictions in Willow Grove system in fall.
(**A**) The PFAS in each diet item were known and provided during the modelling. (**B**) The PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. The dot models values when fish tissue PFAS, water, and sediment values are at their measured mean values. The food web structure was the same between both cases. The dotted lines mark values where data were over- or under-predicted by a factor or 2 (lower line) and 10 (upper line), respectively.

<br/> <br/>


#### 2. Willow Grove (summer)

The model predictions for Willow Grove in summer season.
The temperature was not recorded in water (or not provided in the file), assuming 23 ºC in summer. 
```{r willow grove summer}
source(here("Code", "R data tables", "WG_summer.R")) # medians not same day

# PFAS are known in each diet item
settings_obsDiet = new_Settings(
  chooseDiet = 'forced', # known PFAA in diet
  chooseKoc = 'Koc',
  chooseDmw = "Droge",
  chooseEw = "empirical"
)

# # used below in sed:water est part 
# WG_inputFiles_list<-inputFiles_list
# water_WG<-d.water %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# water_WG<-water_WG/1000
# colnames(water_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# sed_WG<-d.sed %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# colnames(sed_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# obs_ratio_WG<-sed_WG/water_WG


# run the bioaccumulation model: 
AllDataWGsum<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet item are calculated from trophic transfer
settings_modelDiet = new_Settings(
  chooseDiet = 'default',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGsum_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet is set to zero
settings_modelDiet = new_Settings(
  chooseDiet = 'zero',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGsum_zero<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

```

```{r wg summer model bias tables, echo = FALSE, message=FALSE, warning=FALSE}

wg_sum1_error <- estimate_error(MetricData = AllDataWGsum, DataID = "wg_sum_forced", verbose = FALSE)
wg_sum1_error_fw <- estimate_error(MetricData = AllDataWGsum_fw, DataID = "wg_sum_fw", verbose = FALSE)
wg_sum1_error_zero <- estimate_error(MetricData = AllDataWGsum_zero, DataID = "wg_sum_zero", verbose = FALSE)

```

```{r willow grove summer data output and plots, fig.cap= "Figure. 1"}
# median value data
AllDataWGsum <- AllDataWGsum[!c(AllDataWGsum$PFAA == "PFUA" | AllDataWGsum$PFAA == "PFDA"),]
AllDataWGsum_fw <- AllDataWGsum_fw[!c(AllDataWGsum_fw$PFAA == "PFUA" | AllDataWGsum_fw$PFAA == "PFDA"),]
AllDataWGsum_zero <- AllDataWGsum_zero[!c(AllDataWGsum_zero$PFAA == "PFUA" | AllDataWGsum_zero$PFAA == "PFDA"),]

p1<-ggplot(data = AllDataWGsum, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 18, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'summer - forced diet')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sum1_error[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_sum1_error[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")
# p1

p2<-ggplot(data = AllDataWGsum_fw, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 18, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sum1_error_fw[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MG[avg] == .(round(wg_sum1_error_fw[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    ggtitle(label = 'trophic diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")


p0<-ggplot(data = AllDataWGsum_zero, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 18, size = 2, alpha =0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'zero diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sum1_error_zero[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_sum1_error_zero[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")


legend_plot <- ggplot(data = AllDataWGsum_fw,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)
fig1<-cowplot::plot_grid(p1, p2, p0, legend,
                   ncol = 2,
                   nrow = 2,
                   rel_widths = c(1,1),
        labels = c("A", "B", "C", ""))
fig1

ggsave(filename = here("./Figures/WG_summer_fig1.png"), width = 7, height = 7)

```

PFAS predictions in Willow Grove system in summer.
(**A**) The PFAS in each diet item were known and provided during the modelling. (**B**) The PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. The dot models values when fish tissue PFAS, water, and sediment values are at their measured mean values. The food web structure was the same between both cases. The dotted lines mark values where data were over- or under-predicted by a factor or 2 (lower line) and 10 (upper line), respectively.

<br/> <br/>



#### 3. Willow Grove (spring)

The model predictions for Willow Grove in spring season.
The temperature was not recorded in water (or not provided in the file), assuming 10 ºC in spring. 
```{r willow grove spring}
source(here("Code", "R data tables", "WG_spring.R")) # medians not same day

# PFAS are known in each diet item
settings_obsDiet = new_Settings(
  chooseDiet = 'forced', # known PFAA in diet
  chooseKoc = 'Koc',
  chooseDmw = "Droge",
  chooseEw = "empirical"
)

# # used below in sed:water est part 
# WG_inputFiles_list<-inputFiles_list
# water_WG<-d.water %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# water_WG<-water_WG/1000
# colnames(water_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# sed_WG<-d.sed %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# colnames(sed_WG)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# obs_ratio_WG<-sed_WG/water_WG


# run the bioaccumulation model: 
AllDataWGsp<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet item are calculated from trophic transfer
settings_modelDiet = new_Settings(
  chooseDiet = 'default',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGsp_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

# PFAS in each diet is set to zero
settings_modelDiet = new_Settings(
  chooseDiet = 'zero',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataWGsp_zero<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

```

```{r wg spring model bias tables, echo = FALSE, message=FALSE, warning=FALSE}

wg_sp1_error <- estimate_error(MetricData = AllDataWGsp, DataID = "wg_sp_forced", verbose = FALSE)
wg_sp1_error_fw <- estimate_error(MetricData = AllDataWGsp_fw, DataID = "wg_sp_fw", verbose = FALSE)
wg_sp1_error_zero <- estimate_error(MetricData = AllDataWGsp_zero, DataID = "wg_sp_zero", verbose = FALSE)

```

```{r willow grove spring data output and plots, fig.cap= "Figure. 1"}
# median value data
AllDataWGsp <- AllDataWGsp[!c(AllDataWGsp$PFAA == "PFUA" | AllDataWGsp$PFAA == "PFDA"),]
AllDataWGsp_fw <- AllDataWGsp_fw[!c(AllDataWGsp_fw$PFAA == "PFUA" | AllDataWGsp_fw$PFAA == "PFDA"),]
AllDataWGsp_zero <- AllDataWGsp_zero[!c(AllDataWGsp_zero$PFAA == "PFUA" | AllDataWGsp_zero$PFAA == "PFDA"),]

p1<-ggplot(data = AllDataWGsp, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'sprin - forced diet')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sp1_error[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_sp1_error[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")
# p1

p2<-ggplot(data = AllDataWGsp_fw, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sp1_error_fw[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MG[avg] == .(round(wg_sp1_error_fw[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
    ggtitle(label = 'trophic diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")


p0<-ggplot(data = AllDataWGsp_zero, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), linewidth = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), linewidth = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'zero diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(wg_sp1_error_zero[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(wg_sp1_error_zero[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")


legend_plot <- ggplot(data = AllDataWGsp_fw,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)
fig1<-cowplot::plot_grid(p1, p2, p0, legend,
                   ncol = 2,
                   nrow = 2,
                   rel_widths = c(1,1),
        labels = c("A", "B", "C", ""))
fig1

ggsave(filename = here("./Figures/WG_spring_fig1.png"), width = 7, height = 7)

```

PFAS predictions in Willow Grove system in spring.
(**A**) The PFAS in each diet item were known and provided during the modelling. (**B**) The PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. The dot models values when fish tissue PFAS, water, and sediment values are at their measured mean values. The food web structure was the same between both cases. The dotted lines mark values where data were over- or under-predicted by a factor or 2 (lower line) and 10 (upper line), respectively.

<br/> <br/>






#### 4. Joint Base Andrews (spring)

The model predictions for JBA in spring season. This system has 8 fish species, and was samples in spring. 

```{r jba spring all data}
source(here("Code", "R data tables", "JBA_spring.R"))

settings_obsDiet = new_Settings(
  chooseDiet = 'forced',
)

# used below for sed:water estimates
# JBAsp_inputFiles_list<-inputFiles_list
# water_JBAsp<-d.water %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# water_JBAsp<-water_JBAsp/1000
# colnames(water_JBAsp)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# sed_JBAsp<-d.sed %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# colnames(sed_JBAsp)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# obs_ratio_JBAsp<-sed_JBAsp/water_JBAsp


AllDataJBAsp<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)


settings_modelDiet = new_Settings(
  chooseDiet = 'default'
)

AllDataJBAsp_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

AllDataJBAsp <- AllDataJBAsp[!c(AllDataJBAsp$PFAA == "PFUA" ),]
AllDataJBAsp_fw <- AllDataJBAsp_fw[!c(AllDataJBAsp_fw$PFAA == "PFUA" ),]

# PFAS in each diet item is set to zero
settings_modelDiet = new_Settings(
  chooseDiet = 'zero',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataJBAsp_zero<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

```

```{r jba spring model bias tables, echo = FALSE, message=FALSE, warning=FALSE}

jba_sp1_error <- estimate_error(MetricData = AllDataJBAsp, DataID = "jba_sp", verbose = FALSE)
jba_sp1_error_fw <- estimate_error(MetricData = AllDataJBAsp_fw, DataID = "jba_sp_fw", verbose = FALSE)
jba_sp1_error_zero <- estimate_error(MetricData = AllDataJBAsp_zero, DataID = "jba_sp_zero", verbose = FALSE)

```

```{r jba spring figures, fig.cap= "Figure. 2"}

p1<-ggplot(data = AllDataJBAsp, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'spring - forced diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sp1_error[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sp1_error[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")
# p1_fish

p2<-ggplot(data = AllDataJBAsp_fw, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'trophic diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sp1_error_fw[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sp1_error_fw[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")
# p1_fish_re

p0<-ggplot(data = AllDataJBAsp_zero, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 17, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'zero diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sp1_error_zero[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sp1_error_zero[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")

# p1_fish_re
legend_plot <- ggplot(data = AllDataJBAsp_fw,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)

legend<-cowplot::get_legend(legend_plot)
fig1<-cowplot::plot_grid(p1, p2, p0, legend,
                   ncol = 2,
                   nrow = 2,
                   rel_widths = c(1, 1),
        labels = c("A", "B", "C", ""))
fig1

ggsave(filename = here("./Figures/JBAspring_fig1.png"), width = 7, height = 7)


```

PFAS predictions in JBA system in spring season. 
(**A**) The PFAS in each diet item were known and provided during the modelling. (**B**) The PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. The dot models values when fish tissue PFAS, water, and sediment values are at their measured mean values. The food web structure was the same between both cases. The dotted lines mark values where data were over- or under-predicted by a factor or 2 (lower line) and 10 (upper line), respectively. 

<br/> <br/>


#### 5. Joint Base Andrews (summer)

```{r jba summer all data, echo = FALSE, message=FALSE, warning=FALSE}
source(here("Code", "R data tables", "JBA_summer.R"))

settings_obsDiet = new_Settings(
  chooseDiet = 'forced'
)

# used below for sediment water ratio estimates
# JBAsum_inputFiles_list<-inputFiles_list
# water_JBAsum<-d.water %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# water_JBAsum<-water_JBAsum/1000 # original data in ng/L,  conver tto ng/mL
# colnames(water_JBAsum)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# sed_JBAsum<-d.sed %>%  # get the medians from the data
#   select(PFHxS.m, PFOS.m, PFOA.m, PFNA.m) %>% 
#   as.data.frame()
# colnames(sed_JBAsum)<-c("PFHxS", "PFOS", "PFOA", "PFNA") 
# obs_ratio_JBAsum<-sed_JBAsum/water_JBAsum

AllDataJBAsum<-runEcosystemModel(settings = settings_obsDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)


settings_modelDiet = new_Settings(
  chooseDiet = 'default'
)

AllDataJBAsum_fw<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

AllDataJBAsum <- AllDataJBAsum[!c(AllDataJBAsum$PFAA == "PFUA" ),]
AllDataJBAsum_fw <- AllDataJBAsum_fw[!c(AllDataJBAsum_fw$PFAA == "PFUA" ),]


# PFAS in each diet item is set to zero
settings_modelDiet = new_Settings(
  chooseDiet = 'zero',
  chooseKoc = 'Koc',
  chooseDmw = "Droge", # default = "Droge", or use "calculated" 
  chooseEw = "empirical", # default = 'empirical', or use "beta#", where:
  # must be in format: beta#, #beta [# = numeric var, no spaces, no special char]"
)

AllDataJBAsum_zero<-runEcosystemModel(settings = settings_modelDiet,
                  inputFiles_list = inputFiles_list,
                  parameterList = c('C_B','C_WTO','C_s',
                                    'k1','k2','ke','kg','kd', 'kr_est',
                                    'Total Elimination', 'RMR',
                                    "Gill_uptake","Dietary_uptake", "Sediment_uptake",
                                    "Gill_up%", "Diet_up%", 'Sed_up%',
                                    "G_V", "G_D"),
                  PFAA_List = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'),
                  dietData = inputFiles_list$dietData,
                  kRTable = kRTable,
                  min_diet_WTO_C_s = TRUE,
                  min_dietData = inputFiles_list$min_dietData,
                  max_diet_WTO_C_s = TRUE, 
                  max_dietData = inputFiles_list$max_dietData)

```

```{r jba summer model bias tables, echo = FALSE, message=FALSE, warning=FALSE}

# median of recorded values 
jba_sum1_error <- estimate_error(MetricData = AllDataJBAsum, DataID = "jba_sum", verbose = FALSE)
jba_sum1_error_fw <- estimate_error(MetricData = AllDataJBAsum_fw, DataID = "jba_sum_fw", verbose = FALSE)
jba_sum1_error_zero <- estimate_error(MetricData = AllDataJBAsum_zero, DataID = "jba_sum_fw", verbose = FALSE) # no diet 

```

```{r jba plots and outputs, echo = FALSE, message=FALSE, warning=FALSE, fig.cap= "Figure 3"}

p1<-ggplot(data = AllDataJBAsum, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 18, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'summer- forced diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sum1_error[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sum1_error[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+    # coord_cartesian(ylim = c(2,6.5), xlim = c(2,6.5))+
    theme(legend.position = "none")
# p1_fish

p2<-ggplot(data = AllDataJBAsum_fw, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 18, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'trophic diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sum1_error_fw[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sum1_error_fw[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")


p0<-ggplot(data = AllDataJBAsum_zero, aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo, ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo, xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    geom_point(pch = 18, size = 2, alpha = 0.8)+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'zero diet')+
    xlab('Modeled log PFAA (ng/kg)')+
    ylab('Measured log PFAA (ng/kg)')+
    annotate(geom = "text", label = bquote(R^2 == .(round(jba_sum1_error_zero[[3]], 3))),
             x = 0.2, y = 7, size = 4, hjust = 0)+
    annotate(geom = "text", label = bquote(MB[avg] == .(round(jba_sum1_error_zero[[1]], 3))),
             x = 0.2, y = 6, size = 4, hjust = 0)+
  # coord_cartesian(ylim = c(0,6.5), xlim = c(0,6.5))+
    # theme(legend.position = "right")
    theme(legend.position = "none")

# p1_fish_re
legend_plot <- ggplot(data = AllDataJBAsum_fw,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)


fig1<-cowplot::plot_grid(p1, p2, p0,legend,
                   ncol = 2,
                   nrow = 2,
                   rel_widths = c(1, 1),
        labels = c("A", "B", "C", ""))
fig1
ggsave(filename = here("./Figures/JBAsummer_fig1.png"), width = 7, height = 7)

```

PFAS predictions in JBA system in summer season. 
(**A**) The PFAS in each diet item were known and provided during the modelling. (**B**) The PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. The dot models values when fish tissue PFAS, water, and sediment values are at their measured mean values. The food web structure was the same between both cases. The dotted lines mark values where data were over- or under-predicted by a factor or 2 (lower line) and 10 (upper line), respectively.

<br/> <br/>

#### All systems together 

```{r setup2}
# median values
AllDataJBAsp$System<-"AFBC-spring"
AllDataJBAsp_fw$System<-"AFBC-spring"
AllDataJBAsum$System<-"AFBC-summer"
AllDataJBAsum_fw$System<-"AFBC-summer"
AllDataWGsum$System<-"NRP-summer"
AllDataWGsum_fw$System<-"NRP-summer"
AllDataWGsp$System<-"NRP-spring"
AllDataWGsp_fw$System<-"NRP-spring"
AllDataWGfall$System<-"NRP-fall"
AllDataWGfall_fw$System<-"NRP-fall"

AllDataJBAsp$Seasonality<-"spring"
AllDataJBAsp_fw$Seasonality<-"spring"
AllDataJBAsum$Seasonality<-"summer"
AllDataJBAsum_fw$Seasonality<-"summer"
AllDataWGsum$Seasonality<-"summer"
AllDataWGsum_fw$Seasonality<-"summer"
AllDataWGsp$Seasonality<-"spring"
AllDataWGsp_fw$Seasonality<-"spring"
AllDataWGfall$Seasonality<-"fall"
AllDataWGfall_fw$Seasonality<-"fall"

d<-rbind(AllDataJBAsp, AllDataJBAsum,
         AllDataWGfall, AllDataWGsp, AllDataWGsum) # median vals for all recorded sediment and water 
d_fw<-rbind(AllDataJBAsp_fw, AllDataJBAsum_fw,
            AllDataWGfall_fw, AllDataWGsp_fw, AllDataWGsum_fw)# median vals

# save the trophic transfer with median values data
write_csv(x = d_fw, file =here("Data/Model_pred_AllSystems_trophicTrans_medVals.csv"))

d$System<-as.factor(d$System)
d_fw$System<-as.factor(d_fw$System)

# median values 
p1<-ggplot(data = d, aes(x = log_ngkg_re, y = Obs_logngkg,
                         color = PFAA,
                         # fill = PFAA,
                         shape = System))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y, shape = NULL, fill = NULL),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1, shape = NULL, fill = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2, shape = NULL, fill = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3, shape = NULL, fill = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4, shape = NULL, fill = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo,
                      ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.1) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo,
                       xmax = log_ngkg_re + logngkg_re_Up), size = 0.1) +
    geom_text(mapping = aes(label = SppAlias), check_overlap = T, size = 2)+
    geom_point(size = 2, alpha = 1)+
    # facet_grid(.~System)+
    scale_shape_manual(values = c("AFBC-spring" = 24,
                                  "NRP-spring" = 17,
                                "AFBC-summer" = 23,
                                "NRP-summer" = 18,
                                "NRP-fall" = 19))+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    # scale_fill_manual(values = PFAA_cols)+
    ggtitle(label = 'Known PFAA in diet')+
    coord_cartesian(ylim = c(1,7), xlim = c(1,7))

ggformat(p1, y_title = ('Measured log PFAS (ng/kg)'), x_title = 'Modeled log PFAS (ng/kg)', size_text = 12, print = F)
p1<-p1+theme(legend.position = "none")
p1

p2<-ggplot(data = d_fw, aes(x = log_ngkg_re, y = Obs_logngkg,
                            color = PFAA,
                            shape = System))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y, shape = NULL),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo,
                      ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.1) +
    geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo,
                       xmax = log_ngkg_re + logngkg_re_Up), size = 0.1) +
    geom_text(mapping = aes(label = SppAlias), check_overlap = T, size = 2)+
    geom_point(size = 2)+
    # facet_grid(.~System)+
    scale_shape_manual(values = c("AFBC-spring" = 24,
                                  "NRP-spring" = 17,
                                "AFBC-summer" = 23,
                                "NRP-summer" = 18,
                                "NRP-fall" = 19))+
    theme_bw()+
    scale_color_manual(values = PFAA_cols)+
    ggtitle(label = 'Trophic transfer of PFAA')+
    coord_cartesian(ylim = c(1,7), xlim = c(1,7))

ggformat(p2, y_title = ('Measured log PFAS (ng/kg)'), x_title = 'Modeled log PFAS (ng/kg)', size_text = 12, print = F)
p2<-p2+theme(legend.position = "none")

# p1_fish_re
legend_plot <- ggplot(data = d,
         aes(x = log_ngkg_re, y = Obs_logngkg, color = PFAA, shape = System))+
  geom_point()+
  scale_color_manual(values = PFAA_cols)+
    scale_shape_manual(values = c("AFBC-spring" = 24,
                                  "NRP-spring" = 17,
                                "AFBC-summer" = 23,
                                "NRP-summer" = 18,
                                "NRP-fall" = 19))+
  theme(legend.title = element_blank())+
  theme_bw()

legend<-cowplot::get_legend(legend_plot)

# ggsave(cowplot::plot_grid(p1, legend, nrow =1, rel_widths = c(1, 0.4)),
#        height = 3.5, width = 5, filename = here("Figures/ModelPreds_mediand_forcedDiets.png"))
# 
# ggsave(cowplot::plot_grid(p2, legend, nrow =1, rel_widths = c(1, 0.4)),
#        height = 3.5, width = 5, filename = here("Figures/ModelPreds_mediand_ftrophicDiets.png"))

ggsave(cowplot::plot_grid(p1, legend, nrow =1, rel_widths = c(1, 0.4)),
       height = 3.5, width = 5, filename = here("Figures/ModelPreds_mediand_forcedDiets_werror.png"))

ggsave(cowplot::plot_grid(p2, legend, nrow =1, rel_widths = c(1, 0.4)),
       height = 3.5, width = 5, filename = here("Figures/ModelPreds_mediand_ftrophicDiets_werror.png"))


```

PFAS predictions in all systems together.(TOP) PFAS in each diet item were known and provided during the modelling (‘forced diet’). (BOTTOM) PFAS values were estimated based on the food web trophic interactions, the only known PFAS values here were in water and sediment. In each case, model is provided median measured PFAS values in water, sediment, and fish tissue (only for the top plot). The food web structure was the same between both cases. The dotted lines mark log values of 2 and 10 showing where values are over- or under-predicted by a factor or 2 and 10 respectively.

<br/> <br/>
```{r figure for NOAA SG grant may 2024, eval = FALSE}
# modified in jan 6 when more data available
library(RColorBrewer)

getcols<-colorRampPalette(brewer.pal(12, "Paired"))
cols_pfas<-getcols(25)

pfas_names<-c("4:2 FTSA", "6:2 FTSA", "EtFOSA",
              "NMeFOSA", "PFHps", "PFBA",     "PFBS",
              "PFDA","PFHxA","PFHpA" ,   
               "PFODA","PFOA",  "PFHxS",
               "PFOS", "PFPeA", "PFPeS", "PFNA",   "PFTeDA",
              "PFTrDA",   "PFUnA")

p_grant<-ggplot(data = d, aes(x = log_ngkg_re, y = Obs_logngkg,
                         color = PFAA,
                         shape = System))+
    geom_line(data = p_lines, mapping = aes(x = x, y = y, shape = NULL),
              linetype = 1, linewidth = 0.5, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y1, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y2, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y3, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    geom_line(data = p_lines, mapping = aes(x = x, y = y4, shape = NULL),
              linetype = 3, linewidth = 0.2, color = "black")+
    # geom_errorbar(aes(ymin = Obs_logngkg - Obs_logngkg_Lo,
    #                   ymax = Obs_logngkg + Obs_logngkg_Up), size = 0.5) +
    # geom_errorbarh(aes(xmin = log_ngkg_re - logngkg_re_Lo,
    #                    xmax = log_ngkg_re + logngkg_re_Up), size = 0.5) +
    # geom_text(mapping = aes(label = SppAlias), check_overlap = T, size = 2)+
    geom_point(size = 3)+
    # facet_grid(.~System)+
    scale_shape_manual(values = c("AFBC-spring" = 24,
                                  "NRP-spring" = 17,
                                "AFBC-summer" = 23,
                                "NRP-summer" = 18,
                                "NRP-fall" = 19))+
    theme_bw()+
    scale_color_manual(values = cols_pfas, breaks = pfas_names)+
    ggtitle(label = 'Given PFAA diet values')+
    coord_cartesian(ylim = c(1,7), xlim = c(1,7))

ggformat(p_grant, y_title = ('Measured log PFAS (ng/kg)'), x_title = 'Modeled log PFAS (ng/kg)', size_text = 12, print = F)
p_grant<-p_grant+theme(legend.position = "left")
# p_grant



```



#### Error estimates and model bias

```{r error estimates MB all systems together}
getMB<-function(dataList, 
                systemName,
                modelType,
                dataType,
                MBsubset = NULL){
  
    dataList0<-as.data.frame(dataList) 
    dataList0$System<-systemName
    dataList0$Model<-modelType
    dataList0$`Data type`<-dataType
    print(names(dataList0))
    if(MBsubset =="avg"){
      names(dataList0)<- c("MB", "System", "Model", "Data type")
    }
  
return(dataList0)
}

# AFBC summer 
jba_sum1_mb<-getMB(jba_sum1_error[[1]],
                   "AFBC-summer", "known diet","median values", "avg")

jba_sum1_mb_fw<-getMB(jba_sum1_error_fw[[1]],
                      "AFBC-summer", "trophic estimation", "median values", "avg")
# AFBC spring
jba_sp1_mb<-getMB(jba_sp1_error[[1]],
                  "AFBC-spring", "known diet", "median values", "avg")

jba_sp1_mb_fw<-getMB(jba_sp1_error_fw[[1]],
                     "AFBC-spring", "trophic estimation", "median values", "avg")
# WG summer 
wg_sum1_mb<-getMB(wg_sum1_error[[1]],
                   "NRP-summer", "known diet","median values", "avg")

wg_sum1_mb_fw<-getMB(wg_sum1_error_fw[[1]],
                      "NRP-summer", "trophic estimation", "median values", "avg")
# WG spring
wg_sp1_mb<-getMB(wg_sp1_error[[1]],
                  "NRP-spring", "known diet", "median values", "avg")

wg_sp1_mb_fw<-getMB(wg_sp1_error_fw[[1]],
                     "NRP-spring", "trophic estimation", "median values", "avg")
# WG fall
wg_fall1_mb<-getMB(wg_fall1_error[[1]],
                  "NRP-fall", "known diet", "median values", "avg")

wg_fall1_mb_fw<-getMB(wg_fall1_error_fw[[1]],
                     "NRP-fall", "trophic estimation", "median values", "avg")

d_err<-rbind(jba_sum1_mb, jba_sp1_mb,
          wg_fall1_mb, wg_sum1_mb, wg_sp1_mb)
d_err_fw<-rbind(jba_sum1_mb_fw, jba_sp1_mb_fw,
          wg_fall1_mb_fw, wg_sum1_mb_fw, wg_sp1_mb_fw)

```


```{r error estimates MB all systems together}
# Model bias by PFAA using median values 
# AFBC summer 
jba_sum_pfaa_er_fw<-getMB(jba_sum1_error_fw[[5]],
                   "AFBC-summer", "trophic estimation" ,"median values", "PFAA")

jba_sum_pfaa_er<-getMB(jba_sum1_error[[5]],
                   "AFBC-summer", "known diet" ,"median values", "PFAA")

# AFBC spring
jba_sp_pfaa_er_fw<-getMB(jba_sp1_error_fw[[5]],
                   "AFBC-spring", "trophic estimation" ,"median values", "PFAA")

jba_sp_pfaa_er<-getMB(jba_sp1_error[[5]],
                   "AFBC-spring", "known diet" ,"median values", "PFAA")

# NRP summer 
wg_sum_pfaa_er_fw<-getMB(wg_sum1_error_fw[[5]],
                   "NRP-summer", "trophic estimation" ,"median values", "PFAA")

wg_sum_pfaa_er<-getMB(wg_sum1_error[[5]],
                   "NRP-summer", "known diet" ,"median values", "PFAA")

# NRP spring
wg_sp_pfaa_er_fw<-getMB(wg_sp1_error_fw[[5]],
                   "NRP-spring", "trophic estimation" ,"median values", "PFAA")

wg_sp_pfaa_er<-getMB(wg_sp1_error[[5]],
                   "NRP-spring", "known diet" ,"median values", "PFAA")

# NRP fall
wg_fall_pfaa_er_fw<-getMB(wg_fall1_error_fw[[5]],
                   "NRP-fall", "trophic estimation" ,"median values", "PFAA")

wg_fall_pfaa_er<-getMB(wg_fall1_error[[5]],
                   "NRP-fall", "known diet" ,"median values", "PFAA")


d_pfaa_er<-rbind(jba_sum_pfaa_er, jba_sp_pfaa_er, 
                    wg_sum_pfaa_er, wg_sp_pfaa_er, wg_fall_pfaa_er) # median vals, trophic estimationd
d_pfaa_er_fw<-rbind(jba_sum_pfaa_er_fw, jba_sp_pfaa_er_fw,
                    wg_sum_pfaa_er_fw, wg_sp_pfaa_er_fw, wg_fall_pfaa_er_fw) # median vals, trophic estimation


# ***************************************
# Model bias by species 
# AFBC summer 
jba_sum_spp_er_fw<-getMB(jba_sum1_error_fw[[4]],
                   "AFBC-summer", "trophic estimation" ,"median values", "PFAA")

jba_sum_spp_er<-getMB(jba_sum1_error[[4]],
                   "AFBC-summer", "known diet" ,"median values", "PFAA")

# AFBC spring
jba_sp_spp_er_fw<-getMB(jba_sp1_error_fw[[4]],
                   "AFBC-spring", "trophic estimation" ,"median values", "PFAA")

jba_sp_spp_er<-getMB(jba_sp1_error[[4]],
                   "AFBC-spring", "known diet" ,"median values", "PFAA")

# NRP summer 
wg_sum_spp_er_fw<-getMB(wg_sum1_error_fw[[4]],
                   "NRP-summer", "trophic estimation" ,"median values", "PFAA")

wg_sum_spp_er<-getMB(wg_sum1_error[[4]],
                   "NRP-summer", "known diet" ,"median values", "PFAA")

# NRP spring
wg_sp_spp_er_fw<-getMB(wg_sp1_error_fw[[4]],
                   "NRP-spring", "trophic estimation" ,"median values", "PFAA")

wg_sp_spp_er<-getMB(wg_sp1_error[[4]],
                   "NRP-spring", "known diet" ,"median values", "PFAA")

# NRP fall
wg_fall_spp_er_fw<-getMB(wg_fall1_error_fw[[4]],
                   "NRP-fall", "trophic estimation" ,"median values", "PFAA")

wg_fall_spp_er<-getMB(wg_fall1_error[[4]],
                   "NRP-fall", "known diet" ,"median values", "PFAA")


d_spp_er<-rbind(jba_sum_spp_er, jba_sp_spp_er, 
                    wg_sum_spp_er, wg_sp_spp_er, wg_fall_spp_er) # median vals, trophic transferd
d_spp_er_fw<-rbind(jba_sum_spp_er_fw, jba_sp_spp_er_fw,
                    wg_sum_spp_er_fw, wg_sp_spp_er_fw, wg_fall_spp_er_fw) # median vals, trophic transfer


```


```{r display tables of error estimates MB all systems together, eval=TRUE}

# ***************************************
err_data<-rbind(d_err, d_err_fw) # median values
err_pfaa_data<-rbind(d_pfaa_er, d_pfaa_er_fw) # median values, by pfaa
err_spp_data<-rbind(d_spp_er, d_spp_er_fw) # median values, by species

# ***************************************
# display tables MB avg
rbind(err_data) %>%
  pivot_wider(names_from = System, values_from = MB) %>% 
  kbl(digits = 2, caption = "Table 1: Average model bias") %>%
kable_classic(full_width = F, html_font = "Verdana")


```



```{r model bias plots, fig.cap= "Figure 5.", fig.height=20, fig.width=4}
p_mb1<-ggplot(data = err_data,
           aes(x = System, y = MB,
               shape = Model, 
               group = interaction(Model)))+
  geom_point(position = position_dodge(width = 0.5),
           stat = "identity", size=3)+
  # scale_shape_manual()+
  # geom_hline(yintercept = 1, color = "black")+
  # geom_hline(yintercept = c(0.5, 2), color = "black", linetype = 2, linewidth = 0.1)+
  scale_color_manual(values = PFAA_cols)+
  # scale_fill_manual(values = PFAA_cols)+
  theme_bw()+
  # ylim(0,1)+
  theme(legend.position = "top")+
  ylab("Model Bias (tissue conc.)")+
  theme(axis.text.x = element_text(angle = 0))
  # coord_flip(

mb_p2<-err_pfaa_data %>% 
  filter(!PFAA == "PFUA") %>% 
  ggplot(aes(color = System, fill = System,
                                 group = interaction(System, Model),
                                 y = MBavg, x = PFAA))+
  geom_bar(stat = "identity", position='dodge')+
  facet_wrap(.~Model, nrow = 2)+
  scale_color_manual(values = c("AFBC-summer" = "pink2",
                                "AFBC-spring" = "lightgreen",
                                "NRP-summer" = "red4",
                                "NRP-spring" = "green4", 
                                "NRP-fall" = "blue4"))+
  scale_fill_manual(values = c("AFBC-summer" = "pink2",
                                "AFBC-spring" = "lightgreen",
                                "NRP-summer" = "red4",
                                "NRP-spring" = "green4", 
                                "NRP-fall" = "blue4"))+
  theme_bw()+
  geom_hline(yintercept = 1)+
  geom_hline(yintercept = c(0.5, 2), linewidth = 0.1, linetype = 2)
mb_p2
ggsave(mb_p2, height = 5, width = 5.5,
       filename = here("Figures/modelbias_pfaa.png"))

  
```


```{r figures on prediction gaps, fig.cap= "Figure 5.", fig.height=20, fig.width=4}
# JBA spring
# AllDataJBAsp_fw$spp_pfaa<-paste(AllDataJBAsp_fw$PFAA,
#                                 AllDataJBAsp_fw$SppAlias)

# p_errorJBAsp<-ggplot(data = AllDataJBAsp_fw[AllDataJBAsp_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and species")+
#   xlab("")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("JBA Spring (trophic diet)")+
#   theme(plot.margin = unit(c(1,1,-0.5,1), "cm"))
#   # scale_x_discrete(labels = c("JBA \n spring", "JBA \n summer", "Willow \nGrove"))

# p_error2JBAsp<-ggplot(data = AllDataJBAsp_fw[!AllDataJBAsp_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and species")+
#   xlab("Diff b/w obs and meas PFAS (ng/g)")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("")+
#   theme(plot.margin = unit(c(-0.5,1,1,1), "cm"))

# cowplot::plot_grid(p_error, p_error2,
#                    rel_heights = c(0.4, 1), 
#                    nrow = 2, ncol =1)


# JBA summer 
# AllDataJBAsum_fw$spp_pfaa<-paste(AllDataJBAsum_fw$PFAA,
#                                 AllDataJBAsum_fw$SppAlias)
# 
# p_errorJBAsum<-ggplot(data = AllDataJBAsum_fw[AllDataJBAsum_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and sumecies")+
#   xlab("")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("JBA Summer (trophic diet)")+
#   theme(plot.margin = unit(c(1,1,-0.5,1), "cm"))
#   # scale_x_discrete(labels = c("JBA \n sumring", "JBA \n summer", "Willow \nGrove"))
# 
# p_error2JBAsum<-ggplot(data = AllDataJBAsum_fw[!AllDataJBAsum_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and sumecies")+
#   xlab("The difference between observed and measured PFAS (ng/g)")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("")+
#   theme(plot.margin = unit(c(-0.5,1,1,1), "cm"))
# 
# # cowplot::plot_grid(p_error, p_error2,
# #                    rel_heights = c(0.4, 1), 
# #                    nrow = 2, ncol =1)
# 
# 
# # Willow Grove
# AllDataWG_fw$spp_pfaa<-paste(AllDataWG_fw$PFAA,
#                                 AllDataWG_fw$SppAlias)
# 
# p_errorWG<-ggplot(data = AllDataWG_fw[AllDataWG_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and sumecies")+
#   xlab("")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("Willow Grove (trophic diet)")+
#   theme(plot.margin = unit(c(1,1,-0.5,1), "cm"))
#   # scale_x_discrete(labels = c("JBA \n sumring", "JBA \n summer", "Willow \nGrove"))
# 
# p_error2WG<-ggplot(data = AllDataWG_fw[!AllDataWG_fw$PFAA == "PFOS", ],
#            aes(color = PFAA, 
#                x = c(10^Obs_logngkg - 10^log_ngkg_re)/1000,
#                y = reorder(spp_pfaa, c(10^Obs_logngkg - 10^log_ngkg_re)/1000),
#                group = interaction(SppAlias, PFAA),
#                size = `Diet_up%`))+
#   geom_point(pch=19, size=3)+
#   scale_color_manual(values = PFAA_cols)+
#   # scale_fill_manual(values = PFAA_cols)+
#   theme_bw()+
#   # ylim(-15,15)+
#   theme(legend.position = "none")+
#   ylab("PFAS and sumecies")+
#   xlab("The difference between observed and measured PFAS (ng/g)")+
#   theme(axis.text.x = element_text(angle = 0))+
#   ggtitle("")+
#   theme(plot.margin = unit(c(-0.5,1,1,1), "cm"))
# 
# # cowplot::plot_grid(p_error, p_error2,
# #                    rel_heights = c(0.4, 1), 
# #                    nrow = 2, ncol =1)
# 
# 
# cowplot::plot_grid(p_errorJBAsp, p_errorJBAsum, p_errorWG, 
#                    p_error2JBAsp, p_error2JBAsum, p_error2WG, 
#                    rel_heights = c(0.4, 0.4, 0.4, 
#                                    1, 1, 1), 
#                    nrow = 5, ncol =1)
# ggformat(p_mb1, y_title = "Model Bias (tissue conc.)", x_title = "", size_text = 12, print = T)
# p_mb1<- p_mb1 +
#   theme(
#     panel.background = element_rect(fill='transparent'), #transparent panel bg
#     plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
#     panel.grid.major = element_blank(), #remove major gridlines
#     panel.grid.minor = element_blank(), #remove minor gridlines
#     legend.background = element_rect(fill='transparent'), #transparent legend bg
#     legend.box.background = element_rect(fill='transparent') #transparent legend panel
#   )
# p_mb1

# 
# ggsave(filename = "../../Figures/fig2_mb_oct31.png", plot = p_mb1, height = 3.5, width = 6, bg = "transparent")


```


#### NOT USED Sample size of observed values and species specific error

```{r NOT USED sample size of observations and error, fig.width=7, fig.height=3, fig.cap = "Figure 6.", eval=TRUE, include=TRUE}

# n_fish$System <- paste(n_fish$loc, "-", tolower(n_fish$Seasonality), sep = "") # from Monte Carlo data wrangling or setup file
# n_fish[n_fish$System == "WG-fall", "System"] <- "Willow Grove"
# d<-merge(d, n_fish ,by = c("System", "SppAlias"), all.x = TRUE)
# 
# ggplot(d, aes(x = n, y = log_ngkg_re - Obs_logngkg,
#               fill = System, group = System))+
#   facet_grid(.~PFAA)+
#   scale_fill_grey()+
#   # geom_smooth(method = "lm", aes(group = NULL, fill = NULL), color = "black")+
#   geom_point(color = "black", pch=21)+
#   theme_bw()+
#   ylab("Diff bioconc (log(Pred) - log(Obs))")+
#   xlab("The number of samples collected")


```

<!-- The relationship between the number of individuals collected at a given sampling event and the difference between the mean observed tissue concentrations and model predicted concentrations.  -->

```{r the CV fish tissue conc and observation-prediction error, fig.width=9, fig.height=3, fig.cap = "Figure 7."}
# dfish.CV$System <- paste(dfish.CV$loc, "-", tolower(dfish.CV$Seasonality), sep = "") # from Monte Carlo data wrangling or setup file
# dfish.CV[dfish.CV$System == "WG-fall", "System"] <- "Willow Grove"
# d<-merge(d, dfish.CV ,by = c("System", "SppAlias", "PFAA"), all.x = TRUE)
# 
# 
# ggplot(d[c(d$PFAA == "PFHxS" | d$PFAA == "PFNA" |
#            d$PFAA == "PFOS" | d$PFAA == "PFOA"), ], aes(x = fish_cv,
#               y = log_ngkg_re - Obs_logngkg,
#               fill = PFAA,
#               shape = System))+
#   facet_grid(.~PFAA, scales = "free")+
#   scale_fill_manual(values = PFAA_cols)+
#   # geom_smooth(method = "lm",formula = y~x, aes(group = PFAA, fill = NULL), color = "black", se=F,linetype = 2, size =0.5)+
#   geom_point(color = "black", size = 3)+
#   # scale_shape_manual(values = c(21, 22, 23))+
#   theme_bw()+
#   ylab("Diff bioconc (log(Pred) - log(Obs))")+
#   xlab("Coefficient of Var (fish tissue)")
```

```{r percent diet uptake and observation-prediction error, fig.width=9, fig.height=3, fig.cap = "Figure 8."}
# trophic level and error 
ggplot(d, aes(x = `Diet_up%`,
              y = log_ngkg_re - Obs_logngkg,
              fill = PFAA,
              shape = System))+
  facet_grid(.~PFAA, scales = "free")+
  scale_fill_manual(values = PFAA_cols)+
  # geom_smooth(method = "lm",formula = y~x, aes(group = PFAA, fill = NULL), color = "grey", se=T, size =0.5)+
  geom_point(color = "black", size = 3)+
  geom_hline(yintercept = 0, color = "black")+
  scale_shape_manual(values = c(21, 22, 23))+
  theme_bw()+
  ylab("Diff bioconc (log(Pred) - log(Obs))")+
  xlab("% Diet uptake")

```

The relationship between the number of individuals collected at a given sampling event and the difference between the mean observed tissue concentrations and model predicted concentrations. 

<br/> <br/>


#### Contributions to PFAA bioaccumulation via diet and water

```{r setup dataframes add trophic levels and ecology}

# JBA summer
jba_sum_trophic_levels<-data.frame(
  SppAlias = c("Phy", "Dac", "Dar", "Min", "Fal", "Bas", "Mad", "Pum", "Swa"), 
  trophic = c(0,       2.62, 3.75,  2.92,  3.25,  1.5,   3.53,  3.83,  2.5),
  System = c("JBA-summer"),
  loc = "JBA sum")

# JBA spring
jba_sp_trophic_levels<-data.frame(
  SppAlias = c("Phy", "Kil", "Chu", "Dac", "Dar", "Min", "Mad", "Pum", "Swa"), 
  trophic = c(0,       2.5,  3.93,   2.62,  3.75,  2.92,  3.53,  3.83,  2.5),
  System = c("JBA-spring"),
  loc = "JBA sp")

# WG 
wg_trophic_levels<-data.frame(
  SppAlias = c("Phy", "Pry", "Bgl", "Bas"), 
  trophic = c(0,       2.31, 3.08,  3.69),
  System = c("Willow Grove"), 
  loc = "WG")

d_sed<-merge(d,
      rbind(jba_sum_trophic_levels, jba_sp_trophic_levels, wg_trophic_levels),
      by = c("SppAlias", "System"))

AllDataWG_fw$loc<-"WG"
AllDataJBAsp_fw$loc<-"JBA sp"
AllDataJBAsum_fw$loc<-"JBA sum"
AllData_fw<-rbind(AllDataWG_fw, AllDataJBAsp_fw, AllDataJBAsum_fw) # trophic levels only 
AllData_fw <- AllData_fw[!c(AllData_fw$PFAA == "PFUA" ),]

AllData_fw<-merge(AllData_fw,
      rbind(jba_sum_trophic_levels, jba_sp_trophic_levels, wg_trophic_levels),
      by = c("SppAlias", "loc", "System"))

# merge fish ecology "DemersPelag" in the data frame
fish_table<-fish_table[!duplicated(fish_table$SppAlias),]
AllData_fw<-merge(AllData_fw, fish_table, by = "SppAlias")
      

# stackbar dataset
AllData_fw_m<-melt(AllData_fw[, c("SppAlias", "PFAA",
                                  "Gill_up%", "Diet_up%", "Sed_up%",
                            "WB", "C_WTO", "C_s", "loc")],
                id.vars=c("loc","SppAlias", "PFAA", "WB", "C_WTO", "C_s"))

# summarize means for % uptake for each run
mean_d_pct<-AllData_fw_m %>%
dplyr::group_by(PFAA, SppAlias, variable, C_WTO, C_s, WB, loc) %>%
summarize(mean_pct = mean(value),
          sd_pct = sd(value)) 

mean_d_pct_m<-mean_d_pct %>% 
  dplyr::group_by(PFAA, variable, C_WTO, C_s) %>%
  summarize(mean_pct = mean(mean_pct),
          sd_pct = sd(mean_pct)) 
  
# summarize actual values 
mean_d<-AllData_fw %>%
dplyr::group_by(PFAA, SppAlias, loc) %>%
summarize(Gill = mean(`Gill_uptake`),
          Diet = mean(`Dietary_uptake`),
          Sediment = mean(`Sediment_uptake`),
          Elimination = mean(`Total Elimination`), 
          WB = mean(WB)) %>%
pivot_longer(cols = c(Gill, Diet, Sediment, Elimination), names_to = "Path", values_to = "Uptake_g.kg.day")

mean_sd<-AllData_fw %>%
dplyr::group_by(PFAA, SppAlias, loc) %>%
summarize(Gill = sd(`Gill_uptake`),
          Diet = sd(`Dietary_uptake`),
          Sediment = sd(`Sediment_uptake`),
          Elimination = sd(`Total Elimination`),
          WB = mean(WB)) %>%
pivot_longer(cols = c(Gill, Diet, Sediment, Elimination), names_to = "Path", values_to = "Uptake_SD_g.kg.day")

AllData_fw_m2 <- merge(mean_d, mean_sd, all.x = TRUE, by = c("PFAA", "SppAlias", "Path", "loc", "WB"))

# water to sediment PFAS ratio
AllData_fw$sed_wt_pfas_ratio <- AllData_fw$C_s/AllData_fw$C_WTO

# labels chemID
PFAA_List <- data.frame(PFAA = c('PFHxS','PFOS','PFOA','PFNA','PFDA','PFUA'), PFAA_labels = c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA','C11 PFCA'), PFAA_n = c(6,8,8,9,10,11))
AllData_fw<-merge(AllData_fw, PFAA_List, by = "PFAA")

AllData_fw$PFAA_labels<-factor(AllData_fw$PFAA_labels)
AllData_fw$PFAA_labels<-factor(AllData_fw$PFAA_labels,
                               levels = c('C6 PFSA','C8 PFSA','C8 PFCA', 'C9 PFCA','C10 PFCA'))
```


 <br/>

```{r demersal pelagic ecology plots , fig.height= 3.5, fig.cap= "Figure 9.", fig.width=10, eval = TRUE}

p_ecol_obs<-ggplot(data = AllData_fw, aes(y = Obs_logngkg,
                              x = PFAA,
                              color = DemersPelag, 
                              shape = loc))+
  geom_boxplot(mapping = aes(y = Obs_logngkg,
                              x = PFAA,
                              color = DemersPelag, 
                              shape = NULL), 
               position = position_dodge(width = 0.5), width = 0.5, size = 0.2)+
  geom_point(position = position_dodge(width = 0.5))+
  theme_bw()+
  scale_color_manual(values = c("#8c3200", "#00839a"))
  # facet_grid(loc~.)+
  # scale_color_nejm()

p_ecol_pred<-ggplot(data = AllData_fw, aes(y = log_ngkg_re,
                              x = PFAA,
                              color = DemersPelag, 
                              shape = loc))+
  geom_boxplot(mapping = aes(y = log_ngkg_re,
                              x = PFAA,
                              color = DemersPelag, 
                              shape = NULL), 
               position = position_dodge(width = 0.5), width = 0.5, size = 0.2)+
  geom_point(position = position_dodge(width = 0.5))+
  theme_bw()+
  scale_color_manual(values = c("#8c3200", "#00839a"))+
  # scale_color_nejm()+
  theme(legend.position = "none")

cowplot::plot_grid(p_ecol_pred, p_ecol_obs, 
                   ncol = 2, 
                   rel_widths = c(1.2, 1))
  

```


```{r water vs gill figure, eval=TRUE, echo=FALSE, fig.align="center", fig.cap="Figure 10.", fig.height=5, fig.width=9, message=FALSE, warning=FALSE}

p1.jbasp<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy" & mean_d_pct$loc == "JBA sp", ],
       aes( x=mean_pct*100, y=SppAlias, color = variable, fill = variable)) + 
    geom_bar(stat="identity", position = "stack") +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_wrap(loc~PFAA, scales = "free", nrow = 1)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C6FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
    scale_color_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C2FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+  ylab("Species")+
  xlab("% Uptake")+
  # coord_polar()+
  theme_bw()+
  theme(legend.position = "top")

p1.jbasum<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy" & mean_d_pct$loc == "JBA sum", ],
       aes( x=mean_pct*100, y=SppAlias, color = variable, fill = variable)) + 
    geom_bar(stat="identity", position = "stack") +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_wrap(loc~PFAA, scales = "free", nrow = 1)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C6FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
    scale_color_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C2FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+  ylab("Species")+
  xlab("% Uptake")+
  # coord_polar()+
  theme_bw()+
  theme(legend.position = "top")

p1.wg<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy" & mean_d_pct$loc == "WG", ],
       aes( x=mean_pct*100, y=SppAlias, color = variable, fill = variable)) + 
    geom_bar(stat="identity", position = "stack") +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_wrap(loc~PFAA, scales = "free", nrow = 1)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C6FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
    scale_color_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C2FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+  ylab("Species")+
  xlab("% Uptake")+
  # coord_polar()+
  theme_bw()+
  theme(legend.position = "top")

p1.all<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy", ],
       aes( x=mean_pct*100, y=SppAlias, color = variable, fill = variable)) + 
    geom_bar(stat="identity", position = "stack") +
    # geom_errorbarh(data = mean_d_pct[mean_d_pct$variable == "Diet_up%" & !mean_d_pct$SppAlias == "Phy", ],
    #                 aes(xmin=mean_pct*100-sd_pct*100, xmax=mean_pct*100+sd_pct*100), 
    #                 position = "dodge", size = 0.5, height = 0.3, color = "black")+
    facet_grid(loc~PFAA, scales = "free")+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"),
                      values = c("#007445", "#00C6FF", "#915801"),
                      labels=c("Diet","Gill", "Sediment"), 
                      name = "")+
    scale_color_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"),
                       values = c("#007445", "#00C2FF", "#915801"), 
                       labels=c("Diet","Gill", "Sediment"), 
                       name = "")+
  ylab("Species")+
  xlab("% Uptake")+
  # coord_polar()+
  theme_bw()

ggformat(p1.all, y_title = "Species", x_title = "% Uptake",
        title = "Trophic tranfer PFAA", size_text = 12)
p1.all<-p1.all+theme(legend.position = "top")

ggsave(height = 6.8, width = 8, filename = here("Figures/Diet_prop.png"))


```
 

The predicted % contribution from gill uptake and dietary uptake in total PFAS uptake in each fish species in each system. 
JBA sp = Joint Base Andrews, spring season. JBA sum = Joint Base Andrews, summer season. WG = Willow Grove. Species Abbreviations: 
 
 <br/>
 
```{r diet to water uptake one examples JBA summer, fig.width=5, fig.height=10, eval = FALSE}

p_diet_water<-ggplot(mean_d_pct[!mean_d_pct$SppAlias == "Phy" & mean_d_pct$loc == "JBA sum", ],
       aes( x=mean_pct*100, y=SppAlias,
            color = variable,
            fill = variable,
            group = loc)) + 
    geom_bar(stat="identity", position = "stack",
             color = "black",
             stroke = 0.3)+
    facet_wrap(.~PFAA, scales = "free", nrow =5)+
    scale_fill_manual(breaks = c("Diet_up%", "Gill_up%", "Sed_up%"), values = c("#007445", "#00C2FF", "#915801"),
                      labels=c("Diet uptake","Gill uptake", "Sediment uptake"))+
  scale_y_discrete(breaks = c("Swa",
                              "Pum",
                              "Min",
                              "Mad",
                              "Fal",
                              "Dar",
                              "Dac",
                              "Bas"), 
                   labels = c("Swallowtail Shiner",
                              "Pumkinseed",
                              "Mudminnow",
                              "Margined Madtom",
                              "Fallfish",
                              "Darter sp.",
                              "Dace sp.",
                              "Largemouth Bass"))+
  ylab("Species")+
  xlab("% Uptake")+
  theme_bw()+
  theme(legend.position = "right")

ggformat(p_diet_water, y_title = 'Species', x_title = "% Uptake", title = "JBA summer", size_text = 12)
p_diet_water<-p_diet_water+ theme(legend.position = "right")



```

```{r uptake and depuration rates per day, message = FALSE, warning  = FALSE, fig.width=10, fig.height=7,  fig.align = "center", eval = FALSE}
ggplot(AllData_fw_m2[!AllData_fw_m2$SppAlias == "Phy", ],
      aes(fill = Path, x = Uptake_g.kg.day, y = SppAlias, color = Path)) + 
    geom_bar(stat="identity", position = "dodge", color = "white") +
    # geom_pointrange(aes(y = SppAlias,
    #                xmin=`Uptake_%g.kg.day`-`Uptake_SD_%g.kg.day`,
    #                xmax=`Uptake_%g.kg.day`+`Uptake_SD_%g.kg.day`), position = position_dodge(width = 1))+
    facet_wrap(.~PFAA, scales = "free")+
    scale_fill_manual(breaks = c("Diet", "Gill", "Sediment", "Elimination"),
                      values = c("#007445", "#00C2FF", "#915801", "black"),
                      labels=c("Diet uptake","Gill uptake", "Sediment", "Total Elimination"))+
  ylab("Species")+
  xlab("Uptake h/kg/d")+
  theme_bw()+
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.text=element_text(size=15))


```

The modeled uptake rates and elimination of PFAS by each species. 


<br/>

 
```{r chain length order fig 1, fig.cap= "Figure 12.", fig.width=7, fig.height=3.5}
#trophic transfer data
p_diet<-ggplot(AllData_fw[!AllData_fw$SppAlias == "Phy",],
       aes(y=`Diet_up%`*100,
           x = PFAA_labels,
           group = PFAA,
           color = PFAA,
           shape = loc))+
  geom_boxplot()+
  geom_point(size = 3)+
  # facet_wrap(.~loc)+
  scale_color_manual(values = PFAA_cols)+
  # geom_line(linewidth = 0.5)+
  ylim(0,100)+
  theme_bw()+
  xlab("PFAA chain length")+
  ylab("PFAA dietary uptake (%)")+
  theme(axis.text.x = element_text(angle = 45))

p_diet2<-ggplot(data = AllData_fw[c(!AllData_fw$SppAlias =="Phy" ),],
       aes(x = `Diet_up%`, 
           y = log_ngkg_re, 
           color = PFAA,
           shape = loc,
           group  = interaction(PFAA)))+
  geom_point(size = 3)+
  theme_bw()+
  scale_color_manual(values = PFAA_cols)+
  xlab("Dietary uptake (% total)")+
  ylab("Modeled log PFAS (ng/kg)")+
  theme(legend.position = "none")

ggsave(cowplot::plot_grid( p_diet2, p_diet, labels = "AUTO", align = "h", rel_widths = c(1, 1.3)), height = 3.5, width = 8, filename = here("Figures/Diet_perPFAS.png"))
```


The chain length of perfluoroalkyl carboxylic acids (PFCA) and perfluorosulfonic acids (PFSA) and the % diet contribution in total PFAS uptake.
Each dot is species; all systems are presented together. 

<br/>

```{r pfaa chain length order fig2, fig.cap= "Figure 13.", fig.width=7, fig.height=3.5}
ggplot(AllData_fw,
       aes(y= log_ngkg_re,
           x = PFAA_labels,
           group = PFAA, 
           color = PFAA, 
           fill = PFAA))+
  geom_boxplot(width = 0.5, alpha = 0.5)+
  geom_point(size = 3)+
  geom_boxplot(width = 0.5, alpha = 0.5, 
               position = position_nudge(x = 0.3),
               mapping = aes(y= Obs_logngkg,
                           x = PFAA_labels,
                           group = PFAA), fill = NA)+
  geom_point(size = 3, pch=21,fill = NA, 
             position = position_nudge(x = 0.3),
             mapping = aes(y= Obs_logngkg,
                           x = PFAA_labels,
                           group = SppAlias, 
                           color = PFAA))+
  scale_color_manual(values = PFAA_cols)+
  scale_fill_manual(values = PFAA_cols)+
  # geom_line(linewidth = 0.5)+
  theme_bw()+
  xlab("PFAA chain length")+
  ylab("Tissue PFAA bioconcentriotions log(ng/kg)")+
  theme(axis.text.x = element_text(angle = 45))

```

The chain length of perfluoroalkyl carboxylic acids (PFCA) and perfluorosulfonic acids (PFSA) and their tissue bioaccumulation. 
Each dot is species; all systems are presented together. The open circles are observed values, the closed circles are modeled values. 


<br/>

```{r sed water reation and diet uptake n1, eval = FALSE, fig.width=3.5, fig.height=3.5}
means_d<-AllData_fw[!c(AllData_fw$SppAlias == "Phy"),] %>% 
  dplyr:::group_by(loc, PFAA) %>% 
  summarize(mean_pfos = mean(`Diet_up%`), 
            mean_ratio = mean(sed_wt_pfas_ratio), 
            C_s = mean(C_s))
AllData_fw$PFAA_class<-sub(paste('.+(?=.{', 4, '})', sep=''), '', AllData_fw$PFAA_labels, perl=T)

                           
p_sed1<-ggplot(AllData_fw[!c(AllData_fw$SppAlias == "Phy"),],
       aes(y= `Diet_up%`, x = sed_wt_pfas_ratio,
           group = interaction( PFAA),
           shape = loc, 
           fill = PFAA))+
  geom_smooth(method = "lm", formula = y~poly(x,1),
              mapping = aes(y= `Diet_up%`,
                                x = sed_wt_pfas_ratio,
           group = PFAA,
           shape = NULL, 
           fill = NULL, color = PFAA), se = F, linetype = 2,
           linewidth = 0.4, show.legend = F)+
  geom_point( size = 2, show.legend = F)+
  scale_color_manual(values = PFAA_cols)+
  scale_fill_manual(values = PFAA_cols)+
  scale_shape_manual(values = c(22, 21, 23))
ggformat(p_sed1, x_title = ("PFAA sediment:water ratio"),
         y_title = ("% Diet uptake (predicted)"))

p_sed2<-ggplot(AllData_fw[!c(AllData_fw$SppAlias == "Phy"),],
       aes(y=log_ngkg_re, x = sed_wt_pfas_ratio,
           group = interaction( PFAA),
           shape = loc, 
           fill = PFAA))+
  geom_smooth(method = "lm",
              mapping = aes(y=log_ngkg_re,
                            x = sed_wt_pfas_ratio,
           group = PFAA,
           shape = NULL, 
           fill = NULL, color = PFAA), se = F, linetype = 2,
           linewidth = 0.4, show.legend = F)+
  geom_point( pch=21, size = 2)+
  # facet_grid(.~PFAA, scales = "free")+
  scale_color_manual(values = PFAA_cols)+
  scale_fill_manual(values = PFAA_cols)+
  scale_shape_manual(values = c(22, 21, 23))+
  scale_linetype_manual(values = c("dashed", "dotted", "solid"))
ggformat(p_sed2, x_title = ("PFAA sediment:water ratio"),
         y_title = ("Tissue PFAA (ng/kg)"))

cowplot::plot_grid(p_sed1, p_sed2, 
                   rel_widths = c(1,1.3),
                   labels = "AUTO")
# ggsave(height = 3, width = 8, filename = here("Figures/Figure9_part4B.png"))


```

Predicted relationships between sediment:water PFAS ratio and fish tissue bioconcentrations (A), and predicted diet uptake (B). Each dot is a species.


#### The proportion of PFAS predicted uptake just from the water

```{r the percent water uptake to the total observed PFAS}

# confirming the calculations:
# the dietary, gill, and sediment uptake is in ngg
total_uptake <- AllData_fw$Dietary_uptake+
                AllData_fw$Gill_uptake+
                AllData_fw$Sediment_uptake

# sanity check
# all(round(total_uptake / c(AllData_fw$k2+ AllData_fw$ke+ AllData_fw$kg+ AllData_fw$kr_est), 2) == 
# round(AllData_fw$C_B_re/1000, 2)) # cb in ng/kg --> turn into ng/g 

AllData_fw$diet_up_ngg<-AllData_fw$Dietary_uptake /
                                 c(AllData_fw$k2+
                                     AllData_fw$ke+
                                     AllData_fw$kg+
                                     AllData_fw$kr_est)
AllData_fw$gill_up_ngg<-AllData_fw$Gill_uptake /
                                 c(AllData_fw$k2+
                                     AllData_fw$ke+
                                     AllData_fw$kg+
                                     AllData_fw$kr_est)
AllData_fw$perc_diet_up_ngg<- AllData_fw$diet_up_ngg / c(AllData_fw$Obs_ngg) *100
AllData_fw$perc_gill_up_ngg<- AllData_fw$gill_up_ngg / c(AllData_fw$Obs_ngg) *100

# pivot table 
mean_d<-AllData_fw %>%
dplyr::group_by(PFAA, SppAlias, loc) %>%
summarize(gill_up = mean(gill_up_ngg),
          diet_up = mean(diet_up_ngg), 
          obs_up = mean(Obs_ngg)) %>%
pivot_longer(cols = c(gill_up, diet_up, obs_up), names_to = "Path", values_to = "uptake_ngg")


p1<-ggplot(data = mean_d[c(mean_d$Path == "gill_up" | mean_d$Path == "diet_up") & !c(mean_d$SppAlias == "Phy" & mean_d$PFAA == "PFNA"), ],
       aes(x = uptake_ngg, fill = PFAA,
                          y = SppAlias,
                          alpha = Path))+
  geom_bar(stat="identity", position = "stack") +
  geom_bar(data = mean_d[c(mean_d$Path == "obs_up") & !c(mean_d$SppAlias == "Phy"), ], 
           mapping  = aes(x = uptake_ngg, fill = PFAA,
                          y = SppAlias), stat = "identity", 
           alpha = 0, color = "black")+
  theme_bw()+
  scale_alpha_discrete(range=c(0.4,1), labels = c("Diet", "Gill"))+
  facet_grid(loc~PFAA, scales = "free")+
  scale_fill_manual(values = PFAA_cols)


ggformat(p1,  y_title = "Species", x_title = "PFAS tissue conc. (ng/g)",
         title = "Trophic transfer", print = T, size_text = 12)
# ggsave(height = 6.5, width = 9, filename = here("Figures/Figure6_part3.png"))


# water uptake only 
p_water_only<-ggplot(data = mean_d[c(mean_d$Path == "gill_up") & !c(mean_d$SppAlias == "Phy" & mean_d$PFAA == "PFNA"), ],
       aes(x = uptake_ngg, fill = PFAA,
                          y = SppAlias))+
  geom_bar(stat="identity", position = "stack") +
  # geom_bar(data = mean_d[c(mean_d$Path == "obs_up") & !c(mean_d$SppAlias == "Phy"), ], 
           # mapping  = aes(x = uptake_ngg, fill = PFAA,
           #                y = SppAlias), stat = "identity", 
           # alpha = 0, color = "black")+
  theme_bw()+
  scale_alpha_discrete(range=c(0.4,1), labels = c("Diet", "Gill"))+
  facet_grid(loc~PFAA, scales = "free")+
  scale_fill_manual(values = PFAA_cols)
```



```{r SAVED report trophic level and the effect on the diet, fig.height = 7, fig.width = 3.5,  eval = TRUE, fig.cap="Figure 14."}
#unites:  multiply Dietary_uptake by 100 to go from ng.g top ng.kg
p_a<-ggplot(AllData_fw[!AllData_fw$SppAlias == "Phy",], aes(y=diet_up_ngg,
                    x = trophic, fill = PFAA, shape = loc))+ 
  geom_point(size = 2, color = "black", stroke = 0.2, show.legend = TRUE)+
  facet_wrap(PFAA~., scales = "free", ncol = 2)+
  scale_fill_manual(values = PFAA_cols)+
  scale_shape_manual(values = c(22, 21, 23))+
  geom_smooth(method = "lm", se = F, linewidth = 0.5, alpha = 0.5, color = "black")+
  theme_bw()
ggformat(p_a,  x_title = "Trophic level", y_title = "PFAA dietary uptake (ng/g)",
         size_text = 10, print = F)
p_a<-p_a + theme(legend.position = "right")

ggsave(height = 6.4, width = 6.5, filename = here("Figures/DietPerc_PFASuptake.png"))


```
The % uptake that come from diet is positively correlated with total PFAS tissue bioaccumulation.  Each dot is a species. 

```{r PART 5 report trophic level and the effect on the diet, fig.height = 8, fig.width = 7, eval = TRUE, fig.cap="Figure 15."}
# plot in ng/g - first unlog and then go from ng/kg to ng/g
p_b<-ggplot(AllData_fw[!AllData_fw$SppAlias == "Phy",], aes(y=(10^log_ngkg_re)/1000 ,
                    x = trophic, color = PFAA))+
  geom_smooth(method = "lm", se = F, linewidth = 0.5, alpha = 0.5, color = "black")+
  geom_smooth( mapping = aes(y=(10^Obs_logngkg)/1000, x = trophic), color = "black", 
               method = "lm", se = F, linewidth = 0.5, linetype = 2, alpha = 0.5)+
  theme_bw()+  
  geom_point(AllData_fw[!AllData_fw$SppAlias == "Phy",],
             mapping = aes(y=(10^Obs_logngkg)/1000,
                    x = trophic, color = PFAA), pch=21)+
  geom_point()+
  facet_grid(PFAA~loc, scales = "free_y")+
  scale_color_manual(values = PFAA_cols)+
  guides(fill = "none", color = "none")
ggformat(p_b,  x_title = "Trophic level", y_title = "PFAA uptake (ng/g)", size_text = 10, print = F)
p_b<-p_b + theme(legend.position = "right")

cowplot::plot_grid(p_b,
                   ncol = 1,
                   align = "v")  
ggsave(height = 6.5, width = 9, filename = here("Figures/Figure9_part5.png"))

       
```


Dietary PFAS uptake (%) is higher in fish at higher trophic levels.  

<br/>
